The role of advection versus diffusion in intraventricular transport

### 2025-03-06 paper/main.tex
Results 3

\subsection{Validation of the simulations with experimental data}
To validate our computational model, we performed photoconversion experiments
in transgenic zebrafish larvae expressing the secreted Dendra2 in their brain ventricles.
Our photoconversion protocol consisted of the acquisition of a baseline,
before localized exposure to a UV laser (at the ROI 1 location)
that converts Dendra2 from a green to a red emitting fluorescent protein. 
To quantify the transport of photoconverted proteins, we measured and
calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
over time (\Crefpanels{fig:fig3}{a},
$F_0$ being the average fluorescence at baseline).

We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when comparing our
experiments (\Crefpanels{fig:fig3}{a, c}) with
simulation (\Crefpanels{fig:fig3}{b, d}).
Importantly, since the initial condition of the simulation is a mean concentration of zero,
the mean concentration $\cbar$ can be interpreted as the change in mean concentration and
is thus a similar metric to $\Delta F$.
The final values of $\cbar$ in our simulations 0.76, 0.72, 0.82, 0.56 and 0.35
(ROIs 2--6, respectively)
are generally higher than the mean experimental values 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
Notwithstanding similar dynamics, we observe small differences between the experiments and simulation.
For instance, transport in ROIs 2--6 is faster in the simulation and reaches higher final values.
Moreover, the $\cbar$ profiles of ROIs 3--4 are opposite order in
the simulations as compared to the experiments.
Despite observing small differences, the in vivo experiments and
simulations are similar enough to convincingly validate the model.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
    \caption{
    \textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$ 
    in each region of interest (ROI)
    observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
    \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
    simulation of Dendra2 protein transport with
    the diffusion coefficient $D_3$.
    \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
    one representative zebrafish larva.
    Time to $\cbar(t)$ reaches a threshold value of 0.25 for
    a transport simulation with diffusion coefficient $D_3$.
    We have excluded the posterior-most regions of the geometries,
    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
    value of 0.25 in these regions.}
    \label{fig:fig3}
\end{figure}
% Final Delta F values
%0.6322650156762044 ROI 2
%0.7059449124175479 ROI 3
%0.6694500367160006 ROI 4
%0.28986700094045437 ROI 5
%0.18155055624229066 ROI 6
% Final mean c values ROIs 2-6: 0.7637806  0.72025859 0.81903216 0.56204164 0.34926411

>>>>

\subsection{Model validation by comparison with photoconversion experiments}

To validate the model predictions, we performed photoconversion
experiments in transgenic zebrafish larvae expressing the secreted
Dendra2 in their brain ventricles. Our photoconversion protocol
consisted of the acquisition of a baseline fluorescence intensity
$F_0$, before localized exposure to a UV laser (at ROI 1) that
converts Dendra2 from a green- to a red-emitting fluorescent
protein. To quantify the transport of photoconverted proteins, we
measured and calculated the change in fluorescence intensity $\Delta F
= (F(t)-F_0)/F_0$ over time (\Crefpanels{fig:fig3}{a}).

Comparing the intensity changes with the simulated concentration
profiles in ROIs 1--6 (\Crefpanels{fig:fig3}{a, b}) show that the
model predictions agree well with the experimental measurements. We
note minor differences however. The simulated values of $\cbar_i$ at
the final time (0.72, 0.82, 0.56 and 0.35 in ROIs 2--6, respectively)
are generally higher than the corresponding experimental $\Delta F$
values (0.63, 0.71, 0.67, 0.29 and 0.18). Moreover, we observe
differences in the distribution within the middle ventricle,
especially with regard to ROIs 2 and 3. Overall, we note that the time
to reach a 25\% threshold agree well between the model predictions and
experimental values (\Crefpanels{fig:fig3}{c, d}).

%% the $\cbar$ profiles of ROIs 3--4 are opposite order in the
%% simulations as compared to the experiments.

%% Notwithstanding similar dynamics, we observe small differences between
%% the experiments and simulation.

%% For instance, transport in ROIs 2--6 is faster in the simulation and
%% reaches higher final values.

%% We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
%% and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when
%% comparing our experiments (\Crefpanels{fig:fig3}{a, c}) with
%% simulation (\Crefpanels{fig:fig3}{b, d}).

%% Importantly, since the initial condition of the simulation is a mean
%% concentration of zero, the mean concentration $\cbar$ can be
%% interpreted as the change in mean concentration and is thus a similar
%% metric to $\Delta F$.

\begin{figure}%[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
    \caption{
    \textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$ 
    in each region of interest (ROI)
    observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
    \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
    simulation of Dendra2 protein transport with
    the diffusion coefficient $D_3$.
    \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
    one representative zebrafish larva.
    Time to $\cbar(t)$ reaches a threshold value of 0.25 for
    a transport simulation with diffusion coefficient $D_3$.
    We have excluded the posterior-most regions of the geometries,
    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
    value of 0.25 in these regions.}
    \label{fig:fig3}
\end{figure}
% Final Delta F values
%0.6322650156762044 ROI 2
%0.7059449124175479 ROI 3
%0.6694500367160006 ROI 4
%0.28986700094045437 ROI 5
%0.18155055624229066 ROI 6
% Final mean c values ROIs 2-6: 0.7637806  0.72025859 0.81903216 0.56204164 0.34926411
